### 2022-09-06 Journal1/Response4/Response.tex

In the low interference system, the PRB and VNF assignment is obtained straightforwardly, and the first step's problem is power allocation. In the first step of our algorithm with the fixed O-RU association, we have
$\mathcal{T}(\bold{P}^{i},\bold{E}^i,\bold{G}^{i-1}) > \mathcal{T}(\bold{P}^{i-1},\bold{E}^{i-1},\bold{G}^{i-1})$ (strictly increase). 
Because in this step, the problem is reformulated to the power allocation, and the objective function is convex, and the convex functions are Lipschitz monotone contractions. 
However, in the second step of the algorithm, we can show as before that the algorithm is increased, but we can not talk about monotonically increases.
Hence we have
$\mathcal{T}(\bold{P}^{i},\bold{E}^i,\bold{G}^{i}) \geq \mathcal{T}(\bold{P}^{i},\bold{E}^{i},\bold{G}^{i-1})$.
Nevertheless, the objective function is still Lipschitz monotone mapping. 
Accordingly, we have 
$\mathcal{T}(\bold{P}^{i},\bold{E}^i,\bold{G}^{i}) > \mathcal{T}(\bold{P}^{i-1},\bold{E}^{i-1},\bold{G}^{i-1})$.
Therefore the objective function is the strictly ascending
function concerning the number of iterations and has an
upper bound.
Consequently, the algorithm converges to the 
global optimum solution in low interference.

\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comment6:} ``In general, the paper must clarify to "what" is the algorithm converging or the global maximum can be understood by the reader and it can be confusing. ''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
We agree with the reviewer that we must clarify "what" the algorithm converges. 
In Section VI-C-2, we revised the convergence proved of the system and described that the algorithm converged to the local convergence.
Moreover, as mentioned in the previous question, we briefly show that the algorithm can converge to a global convergence in the low interference system.
Moreover, in Fig. 12, we numerically demonstrate our algorithm's global convergence in low interference and describe it in Section VII-C.
Nevertheless, although we didn't demonstrate the unconditional global convergence of our algorithm, we did verify its unconditional local convergence.

\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comment7:} ``Regarding presentation, there are some grammar typos, such as "reformulated as follow" in Section VI.B, second paragraph.  ''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
We are pleased to thank the reviewer for improving the grammar in our paper. We have read the paper one more time and tried to fix any grammar problems in the paper.
\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comment8:} ``Finally, according to IEEE style, tables and algorithms must be placed at top of the page, in addition to figures, which have already been correctly placed.  ''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
It is our pleasure to thank the reviewer for this comment. We agree with the reviewer that the
tables and algorithms need to be moved. As a result, all these mistakes were corrected.
